\plaintitle

### 2017-06-05 papers/IoT2017/prelim.tex
no message

\subsubsection{Smart Meters}
\TODO{measures energy production / consumption}
\TODO{may record energy production / consumption on the ledger or directly report it to the DSO}

\subsection{Requirements}

\subsubsection{Security}
Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
\TODO{ensure correct billing (i.e., prosumer cannot tamper with energy production / consumption or financial balances of any prosumer)}
\TODO{ensure that prosumers cannot back out of trades unilaterally, or tamper with other prosumers trading or bids}
\TODO{ensure that prosumers cannot change policies that are to be set by the DSO for the microgird}
\TODO{impact of node compromise is limited, and can be mitigated (i.e., offending node may be removed)}

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
\TODO{this could destabilize the microgrid, or even the main grid}
Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
\TODO{net amount of energy sold (or bought) by a prosumer is limited (by a constant set by the DSO), where net amount of energy sold is the difference between the amount of energy sold and bought (net amount of energy bought is defined analogously)}
\TODO{energy bids posted by the prosumer are limited in the same way}

\subsubsection{Privacy} 
Energy trading should not compromise the privacy of prosumers.
More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
\TODO{other prosumers should not be able to tell how much energy was consumed / produced by a prosumer, or what bids the prosumer has posted (or with whom the prosumer traded}

>>>>

\subsubsection{Smart Meters}
To measure energy production and consumption, a smart meter must be deployed at each prosumer.
Further, these smart meters must be tamper resistant to prevent prosumers from ``stealing electricity'' by tampering with their meters.
Once a smart meter has measured the amount of energy produced and consumed by the prosumer, it can send this information to the DSO for billing purposes.

\subsection{Requirements}
Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy system.

\subsubsection{Security}
Security requirements primarily ensure that every prosumer is billed correctly, but they also provide necessary prerequisite properties for safety.
%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
More specifically, we require that 
\begin{compactitem}
\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
\item prosumers or outside attackers cannot change microgrid policies that are to be set by the DSO,
\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,
\item financial and physical impact of a compromised or faulty node is limited, and the node can be banned by the DSO.
\end{compactitem}

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
A significant difference between promised and delivered energy production (or consumption) can result in a large gap between actual production and consumption in the microgrid, which threatens the stability of not only the microgrid but also the main power grid.
Consequently, prosumers should not be able to trade large amounts of energy, which they are unlikely to deliver.
%Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
Specifically, we require that
\begin{compactitem}
\item net amount of energy sold (or bought) by a prosumer is upper bounded (by an amount set by the DSO), where the net amount of energy sold is the difference between the amount of energy sold and bought by the prosumer, and the net amount of energy bought is defined analogously,
\item energy bids and asks posted by the prosumer are limited in a similar way.
\end{compactitem}

\subsubsection{Privacy} 
Privacy requirements ensure that the prosumers' privacy is not compromised when they participate in energy trading.
We use non-transactive smart metering as a baseline, and require that the transactive system does not leak any additional information compared to the baseline.
More specifically, we require that
\begin{compactitem}
\item only the corresponding smart meter and the DSO may gain information regarding the amount of energy produced, consumed, bought, or sold by a prosumer,\footnote{Note that this requirement is impossible to satisfy if all other prosumers may collude against one target. However, we can assume that the majority of prosumers are non-colluding.}
\item only the prosumer may know which bids and asks it has posted, and no one can know who traded energy with whom.
\end{compactitem}

### 2017-06-05 papers/IoT2017/solution.tex
no message

In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.

@@

\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
\end{tikzpicture}
\caption{High-level architecture of the proposed solution. Components marked red are introduced to provide privacy in a safe and secure manner. Components marked in blue are typical elements of a decentralized transactive microgrid.}
\label{fig:softwareArchitecture}
\end{figure}

@@

%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
%energy consumption asset} (mixing2);
%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);

\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
\end{figure*}

>>>>

In this section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.

@@

\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\trading algorithm};
\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\controller};
\end{tikzpicture}
\caption{High-level architecture of the proposed solution. Components marked red are introduced to provide privacy in a safe and secure manner. Components marked in blue are typical elements of a decentralized transactive microgrid.}
\label{fig:softwareArchitecture}
\end{figure}

@@

%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\energy bid} (bidstorage);
%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {energy\\bid} (partner);
%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
%energy consumption asset} (mixing2);
%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);

\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\energy bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\bid} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\
\end{figure*}

\subsection{Overview}
We
